DRAFT: Harmonized and trait aggregation paper

### 2020-11-25 Paper/Draft_harmonization_paper.tex
25.11: Minor update

% Discussion on differences between aggregated and assigned traits  
Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is. Indeed, it is questionable whether the aggregation of trait information on species or genus-level to a point estimate on family-level can be an adequate description of a particular trait at all, especially for traits with a high variability. In fact, traits can vary strongly on more precise taxonomic levels than the family-level. For example, Monaghan and Soares found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}. Furthermore, studies focusing on the lability of traits, i.e. how much traits are unconstrained by phylogeny, found that traits of ecological preferences (e.g. thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}. Our analysis showed that disagreement between aggregated and assigned traits was largest for body size and respiration traits. The highest possible difference of 1 between aggregated trait affinities and assigned trait affinities (in total in 6.9 \% of all cases) for the Australian dataset occurred most often for body size large and medium (42.5 \% and 39.2 \% of all cases with a difference of 1, respectively) across all comparisons of aggregated and assigned traits. Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32). 
% Mention that body size is binary coded?
For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1). Respiration via plastron and spiracle showed the highest mean and standard deviation of the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3). 
% Include which traits are more consistent?
% ? How have the aggregation and assignments performed when looking back at the original data?

% Conclude:
% The uncertainty of trait information should be taken into account when developing trait databases and appropriate measures to capture this uncertainty should be established.
% One should be cautious when aggregating traits with an high intra-family variation. 
% Taxonomic determination to more precise taxonomic levels

>>>>

% Discussion on differences between aggregated and assigned traits  
Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is. Aggregation of trait information on species or genus-level to a point estimate on family-level suggests a precision which is not necessarily present, especially not for traits with a high variability or if trait information on species-level is missing. In fact, traits can vary strongly on more precise taxonomic levels than the family-level. For example, Monaghan and Soares found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}. Furthermore, studies focusing on the lability of traits, i.e. how much traits are unconstrained by phylogeny, found that traits of ecological preferences (e.g. thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}. Our analysis showed that disagreement between aggregated and assigned traits was largest for body size and respiration traits. The highest possible difference of 1 between aggregated trait affinities and assigned trait affinities (in total in 6.9 \% of all cases) for the Australian dataset occurred most often for body size large and medium (42.5 \% and 39.2 \% of all cases with a difference of 1, respectively) across all comparisons of aggregated and assigned traits. Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32). A reason for this is also that body size was coded binary. For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1). Respiration via plastron and spiracle showed the highest mean and standard deviation of the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).

% Our attempt to synthesize trait information showed

% Conclude:
% The uncertainty of trait information should be taken into account when aggregating traits is necessary and appropriate measures to capture this uncertainty should be established. 
% ? What measures could this be, e.g. report SD

% Include which traits are more consistent?
% How have the aggregation and assignments performed when looking back at the original data?
